Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction

### 2019-06-24 latex/afm-cs-main.tex
Edits that should have gone in last week.

Our previous work on the $\mu$-path pattern using theoretical
calculations, simulations, and a preliminary implementation,
demonstrates that the approach can achieve scanning time
reduction while maintaining faithful image reconstruction
\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. 
The main contributions of this paper relative to that past work are:
\begin{itemize}
\item We introduce a new reconstruction algorithm which is designed to
minimize the artifacts arising from the structure of the $\mu$-path
scanning pattern. This algorithm is described and compared to existing
reconstruction methods through simulations in Sec. \ref{sec:reconstructionMethods}.
\item In our prior experimental prototype, \cite{braker_hardware_2018} we used very basic integral controllers for all three axes for both raster and $\mu$-path scans. Here, we design compensators for each axis using standard loop-shaping techniques (Sec.~\ref{sec:control}), which result in a substantial increase in closed-loop bandwidth (e.g., 50 Hz to 450~Hz for the $Z$-axis).
We show in Sec.~\ref{sec:ff_control} that one of the limitations of $\mu$-path scanning is the discontinuous $X$-axis reference (e.g., in moving between $\mu$-paths) which excites the cross-coupling modes between the $X$ and $Z$ axes, an affect which neither our prior experimental work nor the numerous simulation studies have accounted for. We mitigate the cross coupling with a feed-forward design.
\item We experimentally compare (Sec. \ref{sec:results}) $\mu$-path scanning to not only full density raster scans but also to course raster scans which are interpolated to a full image. This is in contrast to typical sub-line sampling which takes scan lines at random. The clear advantage to a course raster scan is that it requires no modification to the instrument, only to the post-processing.
\item The bulk of this work is based on experiment, not simulation, in contrast to prior work by ourselves \cite{Luo_nano_2015,maxwell_acc_2014} and others \cite{han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}. Our main focus here is on delineating the practical issues which must be addressed to effectively realize $\mu$-path scanning, which has only seen limited attention in the past.
\end{itemize}

@@

% % The sub-problems in lines 6 and 7 have the form
% % \begin{equation}
% %   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle
% %   g,~x - r\rangle
% % \end{equation}
% % for some vectors $g$ and $r$ and, as shown
% % in~\cite{becker_nesta_2011}, have a closed-form solution given by
% % \begin{align}
% %   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b -
% %     Rq\right| - L\\
% %   q &= r - L^{-1}g\\
% %   p &= \left(I - \frac{\lambda}{\lambda + L}
% %     R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
% % \end{align}

@@

\subsection{Cantilever does not need to fully disengage.}
\todo{Not clear to me yet that friction is useful if I scan parallel
  to cantilever. Also not clear to me that the normal force and shear
  force are orthogonal concepts. Maybe the macroscopic analogy breaks
  down, but thinking of a knife pushed into a surface and then
  dragged...}
In our initial implementation \cite{braker_hardware_2018}, we insisted that the during
tip-retraction (state-5), the cantilever tip should fully break
contact with the surface. Here, we impose no such requirement. Rather,
we change the $Z$-setpoint during tip-retraction to only pull away far
enough that the deflection signal stays low (i.e., below the scanning
setpoint), even while we run across the surface. We choose \rzup so
that the interaction between the tip and sample becomes purely
adhesive. In general, stable imaging in is not possible at \rzup and
complete dis-engagement occasionally occurs. This can be seen in bottom pane of
Fig.~\ref{fig:cs_cycle} during the second $XY$-move (black portion) where the tip detaches partway through the move.
%Fig.~\ref{fig:afm_bd_dinv} which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$ based the current state.
When dis-engagement does occur, the $Z$-axis control loop implements an anti-windup scheme to prevent the control from saturating.

>>>>

Our previous work on the $\mu$-path pattern using theoretical
calculations, simulations, and a preliminary implementation,
demonstrates that the approach can achieve scanning time reduction
while maintaining faithful image reconstruction
\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. The
main contributions of this paper relative to that past work are:
\begin{itemize}
\item We introduce a new reconstruction algorithm which is designed to
  minimize the artifacts arising from the structure of the $\mu$-path
  scanning pattern. This algorithm is described and compared to
  existing reconstruction methods through simulations in Sec.
  \ref{sec:reconstructionMethods}.
\item In our prior experimental prototype, \cite{braker_hardware_2018}
  we used very basic integral controllers for all three axes for both
  raster and $\mu$-path scans. Here, we design compensators for each
  axis using standard loop-shaping techniques
  (Sec.~\ref{sec:control}), which result in a substantial increase in
  closed-loop bandwidth (e.g., 50 Hz to 450~Hz for the $Z$-axis). We
  show in Sec.~\ref{sec:ff_control} that one of the limitations of
  $\mu$-path scanning is the discontinuous $X$-axis reference (e.g.,
  in moving between $\mu$-paths) which excites the cross-coupling
  modes between the $X$ and $Z$ axes, an affect which neither our
  prior experimental work nor the numerous simulation studies have
  accounted for. We mitigate the cross coupling with a feed-forward
  design.
\item We experimentally compare (Sec. \ref{sec:results}) $\mu$-path
  scanning to not only full density raster scans but also to course
  raster scans which are interpolated to a full image. This is in
  contrast to typical sub-line sampling which takes scan lines at
  random. The clear advantage to a course raster scan is that it
  requires no modification to the instrument.
\end{itemize}
In general, our main focus here is on delineating the practical issues which
must be addressed to effectively realize $\mu$-path scanning, which
has only seen limited attention in the past, as most of the prior 
investigation of CS in AFM  have been based purely on simulation
\cite{Luo_nano_2015,maxwell_acc_2014, han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}.

@@

% % The sub-problems in lines 6 and 7 have the form
% % \begin{equation}
% %   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle
% %   g,~x - r\rangle
% % \end{equation}
% % for some vectors $g$ and $r$ and, as shown
% % in~\cite{becker_nesta_2011}, have a closed-form solution given by
% % \begin{align}
% %   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b -
% %     Rq\right| -
% %   L\\
% %   q &= r - L^{-1}g\\
% %   p &= \left(I - \frac{\lambda}{\lambda + L}
% %     R^TR\right)\left(
% %     \frac{\lambda}{L}R^Tb +
% %     q\right).
% % \end{align}

@@

\subsection{Cantilever does not need to fully disengage.}
\todo{Not clear to me yet that friction is useful if I scan parallel
  to cantilever. Also not clear to me that the normal force and shear
  force are orthogonal concepts. Maybe the macroscopic analogy breaks
  down, but thinking of a knife pushed into a surface and then
  dragged...} In our initial implementation
\cite{braker_hardware_2018}, we insisted that the during
tip-retraction (state-5), the cantilever tip should fully break
contact with the surface. Here, we impose no such requirement. Rather,
we change the $Z$-setpoint during tip-retraction to only pull away far
enough that the deflection signal stays low (i.e., below the scanning
setpoint), even while we run across the surface. We choose \rzup so
that the interaction between the tip and sample becomes purely
adhesive. In general, stable imaging in is not possible at \rzup and
complete dis-engagement occasionally occurs. This can be seen in
bottom pane of Fig.~\ref{fig:cs_cycle} during the second $XY$-move
(black portion) where the tip detaches partway through the move.
% Fig.~\ref{fig:afm_bd_dinv} which selects either the scanning
% setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$
% based the current state.
When dis-engagement does occur, the $Z$-axis control loop implements
an anti-windup scheme to prevent the control from saturating.
